---
title: "ETM 640 Team 2 Final Project"
author: "Team 2"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library (magrittr, quietly = TRUE) #Used for pipes/dplyr
library (dplyr, quietly = TRUE)
library (ROI, quietly = TRUE)
library (ROI.plugin.glpk, quietly = TRUE)
library (ompr, quietly = TRUE)
library (ompr.roi, quietly = TRUE)
library (pander, quietly = TRUE)
```

## Team Members

- Christopher Davis
- Brandon Iwasaki
- Taban Yolo
- Niss Lagah

## Final Paper

[Click here](https://docs.google.com/document/d/14RsYIWRkcGrVW3ZvBQ0Zhixd4qoAOTht5TTymMF9xBg/edit) to check out our final paper.

Code for this project is in [GitHub](https://github.com/cwhd/cobot-operations)

## Abstract

Robots are becoming cheaper to build and cobotics (collaborative robotics) [1](http://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.37.7236) are creating new business opportunities. The home cleaning market is projected to reach $33 billion by 2022 [2](https://www.zionmarketresearch.com/news/household-cleaners-market) and is an ideal scenario for cobot cleaning services. There are already a plethora of cleaning robots on the  This paper explores the opportunity from an operations research perspective to determine the ideal configurataion to determine how to package robots together for maximum profitibility, explore which types of robots to invest in based on tarket markets, and the best way to transport them around.

## Scenarios

The following scenarios are explored. First we will figure out based on available robot types what is the most profitable configuration of robots - this will correspond to neighborhoods we will target for marketing. Secondly based on our target market, which robots should we invest in to continue to grow. Finally we will look at transportation costs to determine the ideal location for our robot home bases.

### Scenario 1

A certain configuration of robot is used to clean a certain type of space. For example a house with more bathrooms requires more sink cleaners, a house with carpet needs a special vaccum. We have broken down the configuration needed for each space type into different cleaning packages, where a package represents a certain configuration of robots.

The following data represents our 6 packages available and the robots within them. Note that we already have an idea of how much profit we can make from each package.

Robot Information:
 - Robot 1 is the standard vaccum, used for hardwood floors
 - Robot 2 is the carpet vaccum, not needed if there is no carpet
 - Robot 3 is the sink cleaner, we need more for more bathrooms
 - Robot 4 is the duster drone, we need more for bigger spaces
 - Robot 5 is the window cleaner, we need more for more winds, generally bigger spaces

Package Information:
 - Package 1 covers a 1 bathroom apartment or house, <= 1400 square feet with no carpet
 - Package 2 covers a 1 bathroom apt or house, <= 1400 sq ft with carpet
 - Package 3 no carpet, 1 bathroom
 - Package 4 2 bath, carpet, <= 2300 sq ft
 - Package 5 all carpet 2 bath <= 2000 sq ft
 - Package 6 carpet, 2-3 bath, <= 2000 sq ft


Here is dataa from the CSV files:

```{r}
robotData<-read.csv(file="RobotData.csv") #load the data
packageData<-read.csv(file="packageConfigs.csv", header = T) #load the data

Resources <- as.matrix(packageData[1:5,-1])
AvailableF <- robotData[,c(1,4)]
Available <- as.matrix(AvailableF[,-1])
#Profit <- matrix(packageData[6,-1], 
#              ncol=length(packageData[6,-1]))#,dimnames=c("Profit",ProdNames))

NProd <- ncol(Resources)
NResources <- nrow(robotData)

pander (robotData, caption="Robot Data")
pander (packageData, caption="Package Data")
```

Here is the code and the model with hardcoded data. Ideally we should tweak this so that we're using the data from the CSV files above.

```{r}
#NProd <- 6
#NResources <- 5

#this represents the list of packages
#ProdNames <- lapply(list(rep("Package-",NProd)),paste0,1:NProd) 
                 # Product names: Package-1, Package-2, etc. 

#this represents the robots used in each package configuration
#ResNames<- lapply(list(rep("Robot-",NResources)),paste0,1:NResources) 
                 # Resource names: Robot-1, Robot-2, etc.

#each package has it's own profit amount
Profit <- matrix(c(20, 16, 18, 16, 19, 20), 
              ncol=NProd,dimnames=c("Profit",ProdNames))


#this represents how many of each robot is used in each package
#Resources <- matrix(c( 1,0,2,2,4,
#                       1,1,2,2,4,
#                       1,0,1,2,4,
#                       2,2,3,3,5,
#                       0,2,2,3,3,
#                       1,2,3,4,3), 
#              ncol=NProd,dimnames=c(ResNames,ProdNames))

#this represents the number of robots we have available of each type
#Available <- matrix(c(25, 35, 40, 20,25), 
#              ncol=1,dimnames=c(ResNames,"Available"))

#DisplayResources <- rbind(Resources, Profit)
#pander(DisplayResources, caption="Resources used by each product")
#pander (Available, caption="Amount of each Resource Available")

```

- We have 6 packages, we need to determine which is most profitable

To do this we will set the profitibility of each package, and which robots are in each package. 
maximize profit
decision variables: 6 packages
constraints: number of each type of robot

Now that everything is set up, run the model

```{r}

prodmodel <- MIPModel() %>%
  add_variable (x[i], i=1:NProd, type="continuous", lb=0) %>%
  set_objective (sum_expr(Profit[i] * x[i] , i=1:NProd ), "max") %>%
  add_constraint (sum_expr(Resources[j,i]*x[i], i=1:NProd) # Left hand side of constraint
                  <= Available[j],    # Inequality and Right side of constraint
                  j=1:NResources) %>% # Repeat for each resource, j.  
  solve_model(with_ROI(solver = "glpk"))
  
prodmodel
results.products <- matrix (rep(-1.0,NProd), nrow = NProd, ncol=1,
                            dimnames=c(ProdNames,c("x")))

temp <- get_solution (prodmodel, x[i]) # Extracts optimal values of variables   
results.products <- t(temp [,3] )      # Extracts third column

results.products <- matrix (results.products, nrow = 1, ncol=NProd,
                            dimnames=c(c("x"),ProdNames))  
                                       # Resizes and renames 

pander (results.products, caption = "Optimal Production Plan")

```


## Scenario 2

- Use sensitivity analysis to determine where to invest next

from the first scenario we should know what relative profitability is for each robot. We can then look at the shadow pricing (from week 3) to determine which robots are contributing the most to profitibility and therefore where to invest to grow the company.

For this we need to know the cost of each robot, that way we can determine based on the profitibility of each package, which robots do we need to deliver more of our most profitable packages? This will also help us determine which neighborhoods to target for marketing.

We can find shadow pricing with RDuals:

```{r rduals_3var}
rduals1 <-as.matrix(get_row_duals(prodmodel))
dimnames(rduals1)<-list(c("Robot 1", "Robot 2", "Robot 3", "Robot 4", "Robot 5"), c("Row Duals"))
pander(rduals1,caption="Shadow Prices of Constrained Resources")
```

I think this means Robots 4 and 5 are our primary constrainted resources and we should invest in them to make more $. Let's try to add a few more of robots 4 and 5 to see what happens.

```{r}
#First add a few robots of type 4 and 5
Available <- matrix(c(25, 35, 40, 22,23), 
              ncol=1,dimnames=c(ResNames,"Available"))

#now re-run the model


prodmodel2 <- MIPModel() %>%
  add_variable (x[i], i=1:NProd, type="continuous", lb=0) %>%
  set_objective (sum_expr(Profit[i] * x[i] , i=1:NProd ), "max") %>%
  add_constraint (sum_expr(Resources[j,i]*x[i], i=1:NProd) # Left hand side of constraint
                  <= Available[j],    # Inequality and Right side of constraint
                  j=1:NResources) %>% # Repeat for each resource, j.  
  solve_model(with_ROI(solver = "glpk"))
  
prodmodel2
results.products <- matrix (rep(-1.0,NProd), nrow = NProd, ncol=1,
                            dimnames=c(ProdNames,c("x")))

temp <- get_solution (prodmodel2, x[i]) # Extracts optimal values of variables   
results.products <- t(temp [,3] )      # Extracts third column

results.products <- matrix (results.products, nrow = 1, ncol=NProd,
                            dimnames=c(c("x"),ProdNames))  
                                       # Resizes and renames 

pander (results.products, caption = "Optimal Production Plan")

```

That's interesting. By changing some parameters and running this again we can see that by adding a few more  robots our focus changes from package 5 mixed with package 1, to mostly package 5.

I think this tells us that package 5 is the best package to focus on with the mix of robots we have. With a bit of additional investment we can focus primarily on the building type ideal for configuration 5.

## Scenario 3

- Finally we will do the transportation problem so that we can determine which van to send to which neighborhood




[FOR NOW IGNORE EVERYTHING BELOW THE LINE]

### Location Data

Here is data from Zillow with location information:

```{r}
customerLocationData<-read.csv(file="CustomerLocationData.csv") #load the data
print(paste0(nrow(customerLocationData), " rows"))
print(paste0(ncol(customerLocationData), " columns"))
pander (customerLocationData, caption="Customer Location Data")

```



