---
title: "ETM 640 Team 2 Final Project"
author: "Team 2"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library (magrittr, quietly = TRUE) #Used for pipes/dplyr
library (dplyr, quietly = TRUE)
library (ROI, quietly = TRUE)
library (ROI.plugin.glpk, quietly = TRUE)
library (ompr, quietly = TRUE)
library (ompr.roi, quietly = TRUE)
library (pander, quietly = TRUE)
```

## Team Members

- Christopher Davis
- Brandon Iwasaki
- Taban Yolo
- Niss Lagah

## Final Paper

[Click here](https://docs.google.com/document/d/14RsYIWRkcGrVW3ZvBQ0Zhixd4qoAOTht5TTymMF9xBg/edit) to check out our final paper.

Code for this project is in [GitHub](https://github.com/cwhd/cobot-operations)

## Abstract

Robots are becoming cheaper to build and cobotics (collaborative robotics) [1](http://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.37.7236) are creating new business opportunities. The home cleaning market is projected to reach $33 billion by 2022 [2](https://www.zionmarketresearch.com/news/household-cleaners-market) and is an ideal scenario for cobot cleaning services. There are already a plethora of cleaning robots on the  This paper explores the opportunity from an operations research perspective to determine the ideal configurataion to determine how to package robots together for maximum profitibility, explore which types of robots to invest in based on tarket markets, and the best way to transport them around.

## Scenarios

The following scenarios are explored. First we will figure out based on available robot types what is the most profitable configuration of robots - this will correspond to neighborhoods we will target for marketing. Secondly based on our target market, which robots should we invest in to continue to grow. Finally we will look at transportation costs to determine the ideal location for our robot home bases.

### Scenario 1

A certain configuration of robot is used to clean a certain type of space. For example a house with more bathrooms requires more sink cleaners, a house with carpet needs a special vaccum. We have broken down the configuration needed for each space type into different cleaning packages, where a package represents a certain configuration of robots.

The following data represents our 6 packages available and the robots within them. Note that we already have an idea of how much profit we can make from each package.

Robot Information:
 - Robot 1 is the standard vaccum, used for hardwood floors
 - Robot 2 is the carpet vaccum, not needed if there is no carpet
 - Robot 3 is the sink cleaner, we need more for more bathrooms
 - Robot 4 is the duster drone, we need more for bigger spaces
 - Robot 5 is the window cleaner, we need more for more windows, which we've associated to generally bigger spaces

Package Information:
 - Package 1: 1 bathroom apartment or house, <= 1400 square feet with no carpet
 - Package 2: 1 bathroom apt or house, <= 1400 sq ft with carpet
 - Package 3: no carpet, 1 bathroom
 - Package 4: 2 bath, some carpet, <= 2300 sq ft
 - Package 5: fully or almost fully carpeted, 2 bath <= 2000 sq ft
 - Package 6: fully or almost fully carpeted, 2-3 bath, <= 2000 sq ft


Here is dataa from the CSV files:

```{r}
#load the data
robotData<-read.csv(file="RobotData.csv", header = T) 
packageData<-read.csv(file="packageConfigs.csv", header = T) 

rem_row <- robotData[-6,]

#tweak the loaded data so we can work with it
Packages <- as.matrix(packageData[1:5,-1])
Robot_Inv <- as.matrix(rem_row[1:5,4]) #remove 1 mystery row at the end of the matrix
Profit <- as.matrix(packageData[6,-1])

NPkgs <- ncol(Packages)
NRobot <- nrow(Robot_Inv)

#this represents the list of packages
ProdNames <- lapply(list(rep("Package-",NPkgs)),paste0,1:NPkgs) 
                 # Product names: Package-1, Package-2, etc. 

pander (robotData, caption="Robot Data")
pander (packageData, caption="Package Data")
```

Profit is determined for each package in a formula which is outside of the scope of this paper. It is the difference between the cost of the service to the customer and the cost of the transportation of the robots to the location and as you can see from the data varies between \$87 - \$100 an hour.


```{r}
#This is the code from lesson 2 that shows how to work with hardcoded data. At #this point it's all commented out, I'm just leaving it here for now as a #reference for everyone.

#NProd <- 6
#NResources <- 5

#this represents the list of packages
#ProdNames <- lapply(list(rep("Package-",NProd)),paste0,1:NProd) 
                 # Product names: Package-1, Package-2, etc. 

#this represents the robots used in each package configuration
#ResNames<- lapply(list(rep("Robot-",NResources)),paste0,1:NResources) 
                 # Resource names: Robot-1, Robot-2, etc.

#each package has it's own profit amount
#Profit <- matrix(c(20, 16, 18, 16, 19, 20), 
#              ncol=NProd,dimnames=c("Profit",ProdNames))


#this represents how many of each robot is used in each package
#Resources <- matrix(c( 1,0,2,2,4,
#                       1,1,2,2,4,
#                       1,0,1,2,4,
#                       2,2,3,3,5,
#                       0,2,2,3,3,
#                       1,2,3,4,3), 
#              ncol=NProd,dimnames=c(ResNames,ProdNames))

#this represents the number of robots we have available of each type
#Available <- matrix(c(25, 35, 40, 20,25), 
#              ncol=1,dimnames=c(ResNames,"Available"))

#DisplayResources <- rbind(Resources, Profit)
#pander(DisplayResources, caption="Resources used by each product")
#pander (Available, caption="Amount of each Resource Available")

```

- We have 6 packages, we need to determine which is most profitable

To do this we will set the profitibility of each package, and which robots are in each package. 
maximize profit
decision variables: 6 packages
constraints: number of each type of robot

Variables:
$$P_i$$ -- amount of profit per package
$$R_{i,j}$$ -- number of robots of each robot type available


Algebraicly our optimization model should look like this:

$$
 \begin{split}
 \begin{aligned}
    \text{Maximize  }   &  \sum_{i=1}^{NPkgs} P_i x_i \\
    \text{subject to } & \sum_{j=1}^{NRobot} R_{i,j}x_j \leq A_i \; \forall \; i\\
                       & x_i \geq 0  \; \forall \; i
  \end{aligned}
  \end{split}
  (\#eq:Algebraic Model)
$$


Now that everything is set up, run the model

```{r}
prodmodel <- MIPModel() %>%
  add_variable (x[i], i=1:NPkgs, type="continuous", lb=0) %>% 
  set_objective (sum_expr(Profit[i] * x[i] , i=1:NPkgs ), "max") %>%
  add_constraint (sum_expr(Packages[i,j] * x[j], j=1:NPkgs) 
                  <= Robot_Inv[i],    #
                  i=1:NRobot) %>% # 
  solve_model(with_ROI(solver = "glpk"))
  
prodmodel

temp <- get_solution (prodmodel, x[i]) # Extracts optimal values of variables   
results.products <- t(temp [,3] )      # Extracts third column

results.products <- matrix (results.products, nrow = 1, ncol=NPkgs,
                            dimnames=c(c("x"),ProdNames))  
                                       # Resizes and renames 

pander (results.products, caption = "Optimal package configuation")

```

It appears the model has a distribution of packages. We want to further analyze the potential to expand the business and understand how to add value. Moving to scenario 2.   

## Scenario 2

- Use sensitivity analysis to determine where to invest next

From the first scenario we should know what relative profitability is for each robot. We can then look at the shadow pricing (from week 3) to determine which robots are contributing the most to profitibility and therefore where to invest to grow the company.

For this we need to know the cost of each robot, that way we can determine based on the profitibility of each package, which robots do we need to deliver more of our most profitable packages? This will also help us determine which neighborhoods to target for marketing.

We can find shadow pricing with RDuals:

```{r rduals_3var}
rduals1 <-as.matrix(get_row_duals(prodmodel))
dimnames(rduals1)<-list(c("Robot 1", "Robot 2", "Robot 3", "Robot 4", "Robot 5"), c("Row Duals"))
pander(rduals1,caption="Shadow Prices")
```

In the Row Duals value of shadow pricing we see a couple of interesting things. First is that Robot 1 and Robot 2 have values of 0. This means that if we add additional robots of those types we won't be able to increase profitability since they are not limiting the creation of new additional customer packages. 

On the other hand, Robot 5 and 4 have significant price increases that they can add. 

```{r}
#First five robots of both type 4 and 5
#this represents the robots used in each package configuration

ResNames<- lapply(list(rep("Robot-",NRobot)),paste0,1:NRobot) 
                 # Resource names: Robot-1, Robot-2, etc.

More_Robots <- matrix(c(35, 25, 20, 35, 40), 
              ncol=1,dimnames=c(ResNames,"Available"))

#now re-run the model


prodmodel2 <- MIPModel() %>%
  add_variable (x[i], i=1:NPkgs, type="continuous", lb=0) %>%
  set_objective (sum_expr(Profit[i] * x[i] , i=1:NPkgs ), "max") %>%
  add_constraint (sum_expr(Packages[j,i]*x[i], i=1:NPkgs) # Left hand side of constraint
                  <= More_Robots[j],    # Inequality and Right side of constraint
                  j=1:NRobot) %>% # Repeat for each resource, j.  
  solve_model(with_ROI(solver = "glpk"))
  
prodmodel2 #Brandon checked up to here! 11/27

results.products <- matrix (rep(-1.0,NPkgs), nrow = NPkgs, ncol=1,
                            dimnames=c(ProdNames,c("x")))

temp <- get_solution (prodmodel2, x[i]) # Extracts optimal values of variables   
results.products <- t(temp [,3] )      # Extracts third column

results.products <- matrix (results.products, nrow = 1, ncol=NPkgs,
                            dimnames=c(c("x"),ProdNames))  
                                       # Resizes and renames 

pander (results.products, caption = "Optimal Package Configurations")

```


I think this tells us that package 5 is the best package to focus on with the mix of robots we have. With a bit of additional investment we can focus primarily on the building type ideal for configuration 5.

If we now look at overall profitibility based on what we have;
- We know with our optimal configuration we can clean 8 of house type 5 and 3 of house type 1 at a time
- Cleaning one location and transportation the the next location combined typically takes 2 hours

That means we our profit of $1060 for every 2 hours in an 8 hour work day adds up to \$4,240 per day profit. If we can operate 6 days a week that gets us \$25,440 per week of profit.

If we go back to the number of robots we started with, they represented a total investment of $69,000. At our current profit rate we would make back our investment in less than 3 weeks! Let's take a look at that in R:

```{r}

#multiple the cost by the available amout of robots to get investment, sum it up

AvailableT <- robotData[1:5,c(3,4)] #if you update the number of robots, change this
AvailableT$Cost <- as.numeric(sub("\\$","", AvailableT$Cost))
AvailableT$robotCosts <- AvailableT$Cost * AvailableT$Available
totalCost <- sum(AvailableT$robotCosts)
print(paste0("Total Robot Investment: $",totalCost))

```

## Scenario 3

- Finally we will do the transportation problem so that we can determine which van to send to which neighborhood

```{r}
#Tuesday code added by Brandon

#assuming 1.25 kWh/mi and estimated transportation distances between neighborhoods. 
#made-up electric demand based on roomba usage found online
#made-up electric supply for vehicles, which house internal battery that powers the drive train as well as recharging robot units between services within a neighborhood. 

TransportData <- read.csv("TransportationData.csv")

TransportData

TransCost = as.matrix(TransportData[1:3,2:4])
ElectDmd = as.matrix(TransportData[4,2:4])
BattSupp = as.matrix(TransportData[1:3,5])


TransportationMod <- MIPModel() %>%
  add_variable(x[i,j], i=1:3, j=1:3, type = "binary", lb=0) %>% 
  set_objective(sum_expr(TransCost[i,j] * x[i,j], j=1:3, i=1:3)  , "min") %>%
    add_constraint(x[i,j]*(ElectDmd[j]+TransCost[i,j])
                    <= BattSupp[i],
                    i=1:3, j=1:3) #adds constraint for supply side limitation setup by the conditions of the problem. This is taken into account by using the == in the equality setup. 
   
```


[FOR NOW IGNORE EVERYTHING BELOW THE LINE]

### Location Data

Here is data from Zillow with location information:

```{r}
customerLocationData<-read.csv(file="CustomerLocationData.csv") #load the data
print(paste0(nrow(customerLocationData), " rows"))
print(paste0(ncol(customerLocationData), " columns"))
pander (customerLocationData, caption="Customer Location Data")

```





```{r}
NCust <- customerLocationData
NPack <- results.products[,c(1,5)]
NBasemiles <- customerLocationData$Distance.from.base..miles.
  
prodmodel4 <- MIPModel() %>%
  
  add_variable(x[i,j], i = 1:NCust, j = 1:NPack, type = "integer", lb = 0) %>%
  
  set_objective(sum_expr(NBasemiles[i] * sum_expr(x[i,j], j = 1:NPack), i = 1:NCust ), "min") %>%
  
  add_constraint(NPack >= 0) %>%
  add_constraint(NCust >= 0) %>%
  
   solve_model(with_ROI(solver = "glpk"))
  
prodmodel4
```


